---
output:
  - github_document
  - html_document
always_allow_html: yes
theme: journal
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "70%"
)
```
# jsPhyloSVG htmlwidget

The [jsPhyloSVG](http://jsphylosvg.com) javascript library provides a neat visualization tool for phylogenetic trees. This R package, which has the same name, is a wrapper that builds an [htmlwidget](http://www.htmlwidgets.org/) that allows its use in R, including RMarkdown and Shiny. This is still work in progress.

## Installation

You can install jsPhyloSVG from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("USCBiostats/jsPhyloSVG")
```

## Example

In the following, we present an example of usage of the widget. First, using the [ape](https://cran.r-project.org/package=ape) package, we create a random phylogenetic tree.

```{r loading-packages}
library(ape)
library(jsPhyloSVG)
```

```{r random-tree}
x <- rtree(10)
```

Using the `plot.ape` method, we can get a nice tree drawn with ape:

```{r ape-plot}
plot(x)
```

Using the `jsPhyloSVG` function, we can visualize the same tree but using the Javascript library of the same name, [jsPhyloSVG](http://jsphylosvg.com):


```{r}
jsPhyloSVG(write.tree(x), width = 500)
```


